On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-03-28 docs/mvfits_paper/mvf.tex
Weaken Kerr pertubation approximation statment [3]

These solutions allow \grad{} from generic perturbations to be well approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with the spin $-2$ weighted -2 spheroidal harmonics, $_{-2}S\lmn$.

>>>>

Following the usual treatment, these solutions allow \grad{} from a perturbed Kerr BH at sufficiently late times to be approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with spheroidal harmonics, $_{-2}S\lmn$, of spin weight -2.
